Automated Lensing Learner - I: An automated Strong Lensing Identification Pipeline

### 2017-03-07 ms.tex
Added nLSST10 figure and caption to compare

We first estimate the size of a cell that will contain a coherent arc
feature.  To first order approximation, subdivisions of cells that are
1/100th the area of the entire image should contain coherent arc edges
that span an elongated shape within arc-containing cells.  Therefore,
\wording{we perturb the pixels per cell parameter about (30, 30) for
  the HST-like images, and (4, 4) for the LSST-like images.}

Next, the cells per block parameter determines the normalization of
each cell with respect to the neighboring cell.  In general, this will
downweight arc-like edges in cells that neighbor very bright cells,
such as cells that cover the central lens galaxy.  \wording{We therefore
  vary the cells per block parameter between (1, 1) and (3, 3).}

@@

% Scores vs. regularization on larger train/test set with comparable
% grid search in parameterization
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure}[t]\label{fig:trainsize}
\begin{center}
\includegraphics[width=\columnwidth]{figures/trainsize/LSST10.pdf}
\caption{Solid blue line: AUC for models with varying size of the
  training set for LSST10.  Dotted red line: Train time for that
  model.  The improvement of AUC scales linearly with the log of the
  training set size, but train time roughly scales logarithmically.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

We first estimate the size of a cell that will contain a coherent arc
feature.  To first order approximation, subdivisions of cells that are
1/100th the area of the entire image should contain coherent arc edges
that span an elongated shape within arc-containing cells.  Therefore,
we sample the pixels per cell parameter from (8, 8) to (32, 32) for
the HST-like images, and (3, 3) to (5, 5) for the LSST-like images in
our grid search.

Next, the cells per block parameter determines the normalization of
each cell with respect to the neighboring cell.  In general, this will
downweight arc-like edges in cells that neighbor very bright cells,
such as cells that cover the central lens galaxy.  We therefore vary
the cells per block parameter between (2, 2) and (4, 4) for the
LSST-like images and between (1, 1) and (4, 4) for the HST-like
images.

@@

% Scores vs. regularization on larger train/test set with comparable
% grid search in parameterization
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure}[t]\label{fig:trainsizeLSST10}
\begin{center}
\includegraphics[width=\columnwidth]{figures/trainsize/LSST10.pdf}
\caption{Solid blue line: AUC for models with varying size of the
  training set for LSST10.  Dotted red line: Train time for that
  model.  The improvement of AUC scales linearly with the log of the
  training set size, but train time roughly scales logarithmically.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%            
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure}[t]\label{fig:trainsizenLSST10}
\begin{center}
\includegraphics[width=\columnwidth]{figures/trainsize/nLSST10.pdf}
\caption{Same as Figure~\ref{fig:trainsizeLSST10} for nLSST10.  For
  small trainsize, the nLSST10 performs better than LSST10. }
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
